### 2024-02-16 documentation/thesis/thesis_document.tex
.

The Python \emph{heapq} \cite{heapq} module, which implements a
priority queue, is used for this purpose. The calculated distances from
the \emph{CoG} value of the measurements to are inserted into this
queue. Subsequently, as many elements of the queue are returned as
defined by the \emph{IP\_return\_count} parameter. The actual sorting is
carried out by the queue in the background.

@@

The setup is placed and pre-wired in the temperature chamber 24 hours
before the series of measurements are carried out. The insulated housing
of a \emph{Voron 2.4} 3D printer, which has a separately controlled
internal heating system, is used as the temperature chamber. To verify
the temperature, an additional thermometer \emph{VC-7055BT} is placed on
the base plate. A \emph{10mm} thick \emph{PTFE} insulation plate is
placed between the floor and the sensor base plate to prevent direct and
uneven heating of the base plate by the heated floor.

>>>>

The calculated distances from the \emph{CoG} value of the measurements
to are inserted into a heapq priority queue. Subsequently, as many
elements of the queue are returned as defined by the
\emph{IP\_return\_count} parameter. The actual sorting is carried out by
the queue in the background.

@@

The setup is placed and pre-wired in the temperature chamber 24 hours
before the series of measurements are carried out. The insulated housing
of a \emph{Voron 2.4} 3D printer, which has a separately controlled
internal equipped heating system, is used as the temperature chamber. To
verify the temperature, an additional thermometer \emph{VC-7055BT} is
placed on the base plate. A \emph{10mm} thick \emph{PTFE} insulation
plate is placed between the floor and the sensor base plate to prevent
direct and uneven heating of the base plate by the heated floor.
